Compositional Certified Resource Bounds

### 2014-07-03 paper/main.tex
formatting

\usepackage[utf8]{inputenc} %for utf8 input
\usepackage{amssymb} %for shift symbol
\usepackage{amsmath}
\usepackage{listings} %for code
\usepackage{mathpartir} %for typing rules
\usepackage{microtype} %better micro typing
\usepackage{stmaryrd} %for llbracket
\usepackage{mathabx} % for boxes
\usepackage{graphicx} %to include png images
\usepackage{xcolor} %for colors
\usepackage{url}
\usepackage{enumitem}

@@

\begin{figure*}
\tiny

\begin{tabular}{r|p{2cm}c|p{2cm}c|p{2cm}c|p{1.8cm}|c}

@@

$((((1+1)+1)+((-5+(2{\cdot}y))+(2{\cdot}x)))+(-3+(2{\cdot}y)))+1$ &
$O(n)$ &

Fail &
&

@@

$|\inter 0 x| + |\inter 0 y|$
\\

@@

$((((1+1)+(n+(-1{\cdot}i)))+((n+(n{\cdot}j))+((-1+(-1{\cdot}j)){\cdot}i)))+((n+(n{\cdot}j))+((-1+(-1{\cdot}j)){\cdot}i)))+1$ &
$O(n^2)$ &

$\max(n, 0) + \max(0, (1 + \max(n, 0))) + \max(0, (1 + \max(n, 0)))$ &
$O(n)$ &

@@

$1 + 2 |\inter 0 n|$
\\

@@

Fail &
&

Fail &
&

@@

$1 + 2 |\inter 0 {\code{len}}|$
\\

%--------------------------------------------
\hline \texttt{speed\_pldi09\_fig1.c} &

Fail &
&

$\max(n, 0) + \max(n, 0)$ &
$O(n)$ &

God damn it &

$1 + 2 |\inter 0 n|$
\\

%--------------------------------------------
\hline \texttt{speed\_pldi09\_fig4\_2.c} &

Fail &
&

$((((1+1)+n)+(n+(-1{\cdot}m)))+1)+1$ &
$O(n)$ &

Fail &
&

@@

$1 + 2 |\inter 0 n|$
\\

%--------------------------------------------
\hline \texttt{speed\_pldi09\_fig4\_4.c} &

Fail &
&

$((((1+1)+(-1+m))+((1+n)+(-1{\cdot}m)))+1)+1$ &
$O(n)$ &

Fail &
&

@@

%--------------------------------------------
\hline \texttt{speed\_pldi09\_fig4\_5.c} &

@@

$((((1+1)+(-1+n))+m)+1)+1$ &
$O(n)$ &

Fail &
&

@@

Fail
\\

%--------------------------------------------
\hline \texttt{speed\_pldi10\_ex1.c} &

Fail &
&

Fail &
&

Fail &
&

@@

%--------------------------------------------
\hline \texttt{speed\_pldi10\_ex3.c} &

Fail &
&

$((((1+1)+(-1+n))+(-1+n))+1)+1$ &
$O(n)$ &

$\max(n, 0) + \max(n, 0)$ &
$O(n)$ &

@@

%--------------------------------------------
\hline \texttt{speed\_pldi10\_ex4.c} &

$110 A + 33$ &
$O(n)$ &

Fail &
&

Fail &
&

@@

$1 + 2 |\inter 0 n|$
\\

%--------------------------------------------
\hline \texttt{speed\_popl10\_fig2\_1.c} &

$9a + 9b + 10c + 10d + 7$ &
$O(n)$ &

$(((1+1)+((-1{\cdot}y)+m))+((-1{\cdot}x)+n))+1$ &
$O(n)$ &

$\max(0, (n - x)) + \max(0, (m - y))$ &
$O(n)$ &

$\max(0, n-x) + \max(0, m-y)$ &

$|\inter x n| + |\inter y m|$
\\

%--------------------------------------------
\hline \texttt{speed\_popl10\_fig2\_2.c} &

@@

$(((1+1)+((-1{\cdot}x)+n))+(((-1+(-1{\cdot}z))+(-1{\cdot}x))+(2{\cdot}n)))+1$ &
$O(n)$ &

$\max(0, (\max(0, (x + 1 + -z)) + \max(0, (n - x)))) + \max(0, (n - x))$ &
$O(n)$ &

$\max(0, n-x) + \max(0, n-z)$ &

$|\inter x n| + |\inter z n|$
\\

%--------------------------------------------
\hline \texttt{speed\_popl10\_nested\_multiple.c} &

Fail &
&

$(((1+1)+((-1{\cdot}x)+n))+(((y{\cdot}x)+((-1{\cdot}y){\cdot}n))+(((-1{\cdot}x)+n){\cdot}m)))+1$ &
$O(n^2)$ &

$\max(0, (m - y)) + \max(0, (n - x))$ &
$O(n)$ &

$\max(0, m-y) + \max(0, n-x)$ &

$|\inter x n| + |\inter y m|$
\\

%--------------------------------------------
\hline \texttt{speed\_popl10\_nested\_single.c} &

$48 B + 16$ &
$O(n)$ &

$((((1+1)+((-1+(-1{\cdot}x))+n))+((-1+(-1{\cdot}x))+n))+1)+1$ &
$O(n)$ &

$\max(0, min(n, (n + -1))) + \max(0, min(n, (n + -1)))$ &
$O(n)$ &

@@

%--------------------------------------------
\hline \texttt{speed\_popl10\_sequential\_single.c} &

$21 B + 6$ &
$O(n)$ &

$(((1+1)+((-1{\cdot}x)+n))+((-1{\cdot}x)+n))+1$ &
$O(n)$ &

$\max(n, 0) + \max(n, 0)$ &
$O(n)$ &

@@

%--------------------------------------------
\hline \texttt{speed\_popl10\_simple\_multiple.c} &

$9 C + 10 D + 7$ &
$O(n)$ &

$(((1+1)+((-1{\cdot}y)+m))+((-1{\cdot}x)+n))+1$ &
$O(n)$ &

@@

$|\inter 0 m| + |\inter 0 n|$
\\

%--------------------------------------------
\hline \texttt{speed\_popl10\_simple\_single\_2.c} &

$20 D + 12 C + 17$ &
$O(n)$ &

Fail &
&

@@

$|\inter 0 n| + |\inter 0 m|$
\\

%--------------------------------------------
\hline \texttt{speed\_popl10\_simple\_single.c} &

$4 B + 6$ &
$O(n)$ &

$(((1+1)+((-1{\cdot}x)+n))+((-1{\cdot}x)+n))+1$ &
$O(n)$ &

@@

%--------------------------------------------
\hline \texttt{t07.c} &

@@

$(((1+1)+-1)+x)+1$ &
$O(n)$ &

$\max(x, 0) + \max(0, (y +  2 {\cdot} \max(x, 0))) + \max(0, ( 2 {\cdot} \max(x, 0) + \max(y, 0)))$ &
$O(n)$ &

@@

$1 + 3 |\inter 0 x| + |\inter 0 y|$
\\

@@

$(((1+1)+-1)+(z+(-1{\cdot}y)))+1$ &
$O(n)$ &

$\max(0, (\max(0, (y + -9)) + \max(0, (z - y)))) + \max(0, (z - y))$ &
$O(n)$ &

@@

$1.1 |\inter y z| + 0.1 |\inter 0 y|$
\\

@@

$(((1+1)+((-1{\cdot}y)+x))+((-1{\cdot}y)+x))+1$ &
$O(n)$ &

$\max(0, (x - y))$ &
$O(n)$ &

@@

$(((1+1)+((-1{\cdot}y)+m))+((-1{\cdot}x)+n))+1$ &
$O(n)$ &

$\max(0, (n - x)) + \max(0, (m - y))$ &
$O(n)$ &

@@

$|\inter x n| + |\inter y m|$
\\

@@

$((((1+1)+-1)+(((((-1/2){\cdot}y)+((1/2){\cdot}(y{\cdot}y)))+(((-1/2)+y){\cdot}x))+((1/2){\cdot}(x{\cdot}x))))+-1)+1$ &
$O(n^2)$ &

$\max(x, 0) + \max(0, (\max(x, 0) + \max(y, 0)))$ &
$O(n)$ &

@@

$2 |\inter 0 x| + |\inter 0 y|$
\\

@@

$(((1+1)+(-1+x))+((-1{\cdot}y)+x))+1$ &
$O(n)$ &

Fail &
&

@@

$(((1+1)+((-1+(-99{\cdot}y))+(101{\cdot}x)))+((-1{\cdot}y)+x))+1$ &
$O(n)$ &

Fail &
&

@@

$(((1+1)+(151+k))+(-100+i))+1$ &
$O(n)$ &

$\max(0, (i + -100)) + \max(0, (k + i + 51))$ &
$O(n)$ &

@@

$50 + |\inter {-1} i| + |\inter 0 k|$
\\

@@

$((1+1)+((-1{\cdot}y)+x))+1+((1+1)+(y+(-1{\cdot}x)))+1$ &
$O(n)$ &

$\max(0, (\max(0, (y - x)) + \max(0, (x - y)))) + \max(0, (y - x))$ &
$O(n)$ &

@@

$|\inter x y| + |\inter y x|$
\\

@@

Fail &
&

$\max(0, (1000 +  1000 {\cdot} \max(0, -n) + \max(0, (y + -99)))) + \max(0, -n)$ &
$O(n)$ &

@@

$0.1|\inter n y| + 11 |\inter n 0|$
\\

@@

$(((1+1)+-1)+((-1{\cdot}y)+x))+1$ &
$O(n)$ &

$\max(0, ( 1000 {\cdot} \max(0, (x - y)) + \max(y, 0))) + \max(0, (x - y)) + \max(0, -x)$ &
$O(n)$ &

@@

$|\inter x 0| + |\inter 0 y| + 1002 |\inter y x|$
\\

@@

Fail &
&

$\max(0, (1 + \max(x, y, 0)))$ &
$O(n)$ &

@@

$3 + 2 |\inter 0 x| + |\inter 0 y|$
\\

@@

$1.33 + 0.67 |\inter z y|$
\\

@@

$(((1+1)+n)+1)+1$ &
$O(n)$ &

@@

$1 + |\inter 0 n|$
\\

%--------------------------------------------
\end{tabular}
\caption{That big ugly table}
\label{fig:eval}
\end{figure*}

>>>>

\usepackage[utf8]{inputenc} %for utf8 input
\usepackage{amssymb} %for shift symbol
\usepackage{amsmath}
\usepackage{listings} %for code
\usepackage{mathpartir} %for typing rules
\usepackage{microtype} %better micro typing
\usepackage{stmaryrd} %for llbracket
\usepackage{mathabx} % for boxes
\usepackage{graphicx} %to include png images
\usepackage{xcolor} %for colors
\usepackage{url}
\usepackage{enumitem}
\usepackage{array} %for stupid tables

@@

\begin{figure*}
\small

\newcommand{\dir}[2]{\texttt{#1} \\ \texttt{#2}}
\newcommand{\file}[2][c]{%
  \begin{tabular}[#1]{@{}r@{}}#2\end{tabular}}
\renewcommand{\max}[0]{{\rm mx}}
\renewcommand{\min}[0]{{\rm mn}}

\newcolumntype{C}[1]{>{\centering\let\newline\\\arraybackslash\hspace{0pt}}m{#1}}

\centering
\begin{tabular}{r|C{1.1cm}c|C{1.8cm}c|C{1.9cm}c|C{1.8cm}|C{2.65cm}}

@@

% $((((1+1)+1)+((-5+(2{\cdot}y))+(2{\cdot}x)))+(-3+(2{\cdot}y)))+1$ &
$(((2{+}1)\dots$ &
$O(n)$ &

--- &
&

@@

$|\inter 0 x| {+} |\inter 0 y|$
\\

@@

% $((((1+1)+(n+(-1{\cdot}i)))+((n+(n{\cdot}j))+((-1+(-1{\cdot}j)){\cdot}i)))+((n+(n{\cdot}j))+((-1+(-1{\cdot}j)){\cdot}i)))+1$ &
$(((2{+}(n{+} \dots$ &
$O(n^2)$ &

% $\max(n, 0) + \max(0, (1 + \max(n, 0))) + \max(0, (1 + \max(n, 0)))$ &
$\max(n, 0) \dots$ &
$O(n)$ &

@@

$1 {+} 2 |\inter 0 n|$
\\

@@

--- &
&

--- &
&

@@

$1 {+} 2 |\inter 0 {\code{len}}|$
\\

%--------------------------------------------
% \hline \file{\dir{speed\_pldi09}{fig1.c}} &
% 
% ? &
% &
% 
% --- &
% &
% 
% $2 \max(n, 0)$ &
% $O(n)$ &
% 
% God damn it &
% 
% $1 + 2 |\inter 0 n|$
% \\

%--------------------------------------------
\hline \file{\dir{speed\_pldi09}{fig4\_2.c}} &

--- &
&

% $((((1+1)+n)+(n+(-1{\cdot}m)))+1)+1$ &
$(((2{+}n)\dots$ &
$O(n)$ &

--- &
&

@@

$1 {+} 2 |\inter 0 n|$
\\

%--------------------------------------------
\hline \file{\dir{speed\_pldi09}{fig4\_4.c}} &

--- &
&

% $((((1+1)+(-1+m))+((1+n)+(-1{\cdot}m)))+1)+1$ &
$(((2{+}(-1\dots$ &
$O(n)$ &

--- &
&

@@

%--------------------------------------------
\hline \file{\dir{speed\_pldi09}{fig4\_5.c}} &

@@

% $((((1+1)+(-1+n))+m)+1)+1$ &
$(((2{+}(-1\dots$ &
$O(n)$ &

--- &
&

@@

---
\\

%--------------------------------------------
\hline \file{\dir{speed\_pldi10}{ex1.c}} &

--- &
&

--- &
&

--- &
&

@@

%--------------------------------------------
\hline \file{\dir{speed\_pldi10}{ex3.c}} &

--- &
&

% $((((1+1)+(-1+n))+(-1+n))+1)+1$ &
$(((2{+}(-1\dots$ &
$O(n)$ &

$2{\cdot}\max(n, 0)$ &
$O(n)$ &

@@

%--------------------------------------------
\hline \file{\dir{speed\_pldi10}{ex4.c}} &

$110 a + 33$ &
$O(n)$ &

--- &
&

--- &
&

@@

$1 {+} 2 |\inter 0 n|$
\\

%--------------------------------------------
\hline \file{\dir{speed\_popl10}{fig2\_1.c}} &

$9a + 9b + \dots$ &
$O(n)$ &

% $(((1+1)+((-1{\cdot}y)+m))+((-1{\cdot}x)+n))+1$ &
$((2{+}((-y\dots$ &
$O(n)$ &

$\max(0, n {-} x) + \max(0, m {-} y)$ &
$O(n)$ &

$\max(0, n{-}x) + \max(0, m{-}y)$ &

$|\inter x n| {+} |\inter y m|$
\\

%--------------------------------------------
\hline \file{\dir{speed\_popl10}{fig2\_2.c}} &

@@

% $(((1+1)+((-1{\cdot}x)+n))+(((-1+(-1{\cdot}z))+(-1{\cdot}x))+(2{\cdot}n)))+1$ &
$((2{-}x\dots$ &
$O(n)$ &

% $\max(0, (\max(0, (x {+} 1 {+} -z)) + \max(0, (n - x)))) + \max(0, (n - x))$ &
$\max(0, (x + 1 {-}z)\dots$ &
$O(n)$ &

$\max(0, n{-}x) + \max(0, n{-}z)$ &

$|\inter x n| {+} |\inter z n|$
\\

%--------------------------------------------
\hline \file{\dir{speed\_popl10}{nstd\_multiple.c}} &

--- &
&

% $(((1+1)+((-1{\cdot}x)+n))+(((y{\cdot}x)+((-1{\cdot}y){\cdot}n))+(((-1{\cdot}x)+n){\cdot}m)))+1$ &
$((2{-}x{+}n\dots$ &
$O(n^2)$ &

$\max(0, m {-} y) + \max(0, n {-} x)$ &
$O(n)$ &

$\max(0, m{-}y) + \max(0, n{-}x)$ &

$|\inter x n| {+} |\inter y m|$
\\

%--------------------------------------------
\hline \file{\dir{speed\_popl10}{nstd\_single.c}} &

$48 b + 16$ &
$O(n)$ &

% $((((1+1)+((-1+(-1{\cdot}x))+n))+((-1+(-1{\cdot}x))+n))+1)+1$ &
$(((1{-}x{+}n\dots$ &
$O(n)$ &

$\max(0, \! n {-} 1)\dots$ &
$O(n)$ &

@@

%--------------------------------------------
\hline \file{\dir{speed\_popl10}{sqntl\_single.c}} &

$21 b + 6$ &
$O(n)$ &

% $(((1+1)+((-1{\cdot}x)+n))+((-1{\cdot}x)+n))+1$ &
$((2{}-x{+}n\dots$ &
$O(n)$ &

$2{\cdot}\max(n, 0)$ &
$O(n)$ &

@@

%--------------------------------------------
\hline \file{\dir{speed\_popl10}{smpl\_multiple.c}} &

$9 c + 10 d + 7$ &
$O(n)$ &

% $(((1+1)+((-1{\cdot}y)+m))+((-1{\cdot}x)+n))+1$ &
$((2{-}y{+}m\dots$ &
$O(n)$ &

@@

$|\inter 0 m| {+} |\inter 0 n|$
\\

%--------------------------------------------
\hline \file{\dir{speed\_popl10}{smpl\_single2.c}} &

$20 d + 12 c + 17$ &
$O(n)$ &

--- &
&

@@

$|\inter 0 n| {+} |\inter 0 m|$
\\

%--------------------------------------------
\hline \file{\dir{speed\_popl10}{smpl\_single.c}} &

$4 b + 6$ &
$O(n)$ &

% $(((1+1)+((-1{\cdot}x)+n))+((-1{\cdot}x)+n))+1$ &
$((2{-}x{+}n\dots$ &
$O(n)$ &

@@

%--------------------------------------------
\hline \file{\texttt{t07.c}} &

@@

$2+x$ &
$O(n)$ &

% $\max(x, 0) + \max(0, (y +  2 {\cdot} \max(x, 0))) + \max(0, ( 2 {\cdot} \max(x, 0) + \max(y, 0)))$ &
$\max(x, 0)\dots$ &
$O(n)$ &

@@

$1 {+} 3 |\inter 0 x| {+} |\inter 0 y|$
\\

@@

% $(((1+1)+-1)+(z+(-1{\cdot}y)))+1$ &
$((2{+}z{-}y\dots$ &
$O(n)$ &

% $\max(0, (\max(0, (y + -9)) + \max(0, (z - y)))) + \max(0, (z - y))$ &
$\max(0, \! y{-}9)\dots$ &
$O(n)$ &

@@

$1.1 |\inter y z| {+} 0.1 |\inter 0 y|$
\\

@@

% $(((1+1)+((-1{\cdot}y)+x))+((-1{\cdot}y)+x))+1$ &
$((2{-}y{+}x\dots$ &
$O(n)$ &

$\max(0, x {-} y)$ &
$O(n)$ &

@@

% $(((1+1)+((-1{\cdot}y)+m))+((-1{\cdot}x)+n))+1$ &
$((2{-}y{+}m\dots$ &
$O(n)$ &

$\max(0, n {-} x)) + \max(0, m {-} y)$ &
$O(n)$ &

@@

$|\inter x n| {+} |\inter y m|$
\\

@@

% $((((1+1)+-1)+(((((-1/2){\cdot}y)+((1/2){\cdot}(y{\cdot}y)))+(((-1/2)+y){\cdot}x))+((1/2){\cdot}(x{\cdot}x))))+-1)+1$ &
$(((1{+}y^2/2\dots$ &
$O(n^2)$ &

$2{\cdot}\max(x, 0) + \max(y, 0)$ &
$O(n)$ &

@@

$2 |\inter 0 x| {+} |\inter 0 y|$
\\

@@

% $(((1+1)+(-1+x))+((-1{\cdot}y)+x))+1$ &
$((1{+}x\dots$ &
$O(n)$ &

--- &
&

@@

% $(((1+1)+((-1+(-99{\cdot}y))+(101{\cdot}x)))+((-1{\cdot}y)+x))+1$ &
$((-99{\cdot}y\dots$ &
$O(n)$ &

--- &
&

@@

% $(((1+1)+(151+k))+(-100+i))+1$ &
$((153{+}k\dots$ &
$O(n)$ &

$\max(0, \! i{-}10^2) \!+ \max(0, \! k {+} i {+} 51)$ &
$O(n)$ &

@@

$50 {+} |\inter {-1} i| {+} |\inter 0 k|$
\\

@@

% $((1+1)+((-1{\cdot}y)+x))+1+((1+1)+(y+(-1{\cdot}x)))+1$ &
$(2{-}y{+}x\dots$ &
$O(n)$ &

% $\max(0, (\max(0, (y - x)) + \max(0, (x - y)))) + \max(0, (y - x))$ &
$2 {\cdot} \max(0, \! y {-} x) \! + \max(0, \! x {-} y)$ &
$O(n)$ &

@@

$|\inter x y| {+} |\inter y x|$
\\

@@

--- &
&

% $\max(0, (1000 +  1000 {\cdot} \max(0, -n) + \max(0, (y + -99)))) + \max(0, -n)$ &
$10^3 \max(0, \discretionary{}{}{} -n) \! \dots$ &
$O(n)$ &

@@

$0.1|\inter n y| {+} 11 |\inter n 0|$
\\

@@

% $(((1+1)+-1)+((-1{\cdot}y)+x))+1$ &
$((1{-}y{+}x\dots$ &
$O(n)$ &

% $\max(0, ( 1000 {\cdot} \max(0, (x - y)) + \max(y, 0))) + \max(0, (x - y)) + \max(0, -x)$ &
$10^3 \,\max(0, x - y)\dots$ &
$O(n)$ &

@@

$|\inter x 0| {+} |\inter 0 y| \discretionary{}{}{} {+} 1002 |\inter y x|$
\\

@@

--- &
&

$1 + \max(x, y)$ &
$O(n)$ &

@@

$3 {+} 2 |\inter 0 x| {+} |\inter 0 y|$
\\

@@

$1.33 {+} 0.67 |\inter z y|$
\\

@@

$4+n$ &
$O(n)$ &

@@

$1 {+} |\inter 0 n|$
\\

%--------------------------------------------
\end{tabular}
\caption{
  Experimental evaluation comparing the bounds generated KoAT, Rank,
  Loopus, Speed, and our automatic amortized analysis on several
  challenging linear examples. Results for KoAT and Speed were extracted
  from older publications because KoAT cannot take C programs as 
  input in its current version and Speed is not publically available.
  Entries marked with ? signal that we cannot test the tool. Entries
  marked with --- mean that the tool failed to produce a result.
}
\label{fig:eval}
\end{figure*}
